Reducing Linearizability of Priority Queues and More Data Structures to State Reachability

### 2017-04-19 introduction.tex
intro sketch
added references to the intro

Efficient implementations of concurrent objects are hard to get right. Verifying them is difficult, checking a single execution is NP-complete~\cite{journals/siamcomp/GibbonsK97} and checking a finite-state implementation is undecidable~\cite{conf/esop/BouajjaniEEH13}.

@@

Here, we consider another important object, the priority queues, which are used to TODO, and for which numerous implementations exist CITE (research articles and languages/libraries providing priority queue implementations). This object is much less studied compared to the other ones in the verification literature.

>>>>

Efficient implementations of concurrent objects are essential and hard to get right. Verifying them is difficult, checking a single execution is NP-complete~\cite{journals/siamcomp/GibbonsK97} and checking a finite-state implementation is undecidable~\cite{conf/esop/BouajjaniEEH13}.

@@

Here, we consider another important object, the priority queues, which are essential for applications such as task scheduling and discrete event simulation, and for which numerous implementations have been proposed, e.g.,~\cite{DBLP:conf/ppopp/AlistarhKLS15,DBLP:conf/wdag/CalciuMH14,DBLP:conf/opodis/LindenJ13,DBLP:conf/podc/ShavitZ99,DBLP:conf/ipps/ShavitL00}. This object is much less studied compared to the other ones in the verification literature.
